Minimizing Time Required For Graduation

### 2010-12-06 paper/paper.tex
Fixed an equation reference

\subsubsection{Formulation as Binary Integer Program} We can now formulate our
problem as a binary linear programming problem. Before stating the linear
program, we must first define some variables used in it: \\ \begin{itemize}
\item $ X_i = \left\{ \begin{array}{lr} 1 \text{ if we take } X_i\\ 0 \text{ if
we don't take } X_i \end{array} \right. $ \item For all $t \in O$, we let $t
= 1$.  \item Let $m = \|L\|$.  \end{itemize} We now state our problem as
follows:

@@

Each of the equations based on eqn. 2 ensure that we only take one class per 
time period per day. Also this linear program is ‘nice’ in that it always has 
feasible origin (don’t take any classes), and that the simplest formulation 
is already in standard form.

>>>>

\subsubsection{Formulation as Binary Integer Program} We can now formulate
a binary linear programming problem. Before stating the linear
program, we must first define some variables used in it: \\ \begin{itemize}
\item $ X_i = \left\{ \begin{array}{lr} 1 \text{ if we take } X_i\\ 0 \text{ if
we don't take } X_i \end{array} \right. $ \item For all $t \in O$, we let $t
= 1$.  \item Let $m = \|L\|$.  \end{itemize} We now state our problem as
follows:

@@

Each of the equations based on eqn.~\ref{time_con} ensure that we only take one class per 
time period per day. Also this linear program is ‘nice’ in that it always has 
feasible origin (don’t take any classes), and that the simplest formulation 
is already in standard form.
